 \documentclass[a4paper]{tufte-book}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{longtable} 
\usepackage{lscape}
\usepackage{colortbl}

\geometry{
  left=.5in,
  right=.5in,
  top=.5in,
  bottom=.5in
}

\begin{document}

\begin{landscape}
\advance\vsize6cm
\csname @colroom\endcsname=\vsize
\textheight=\vsize
\csname @colht\endcsname=\vsize

\setlength{\parindent}{0em}
\setlength{\parskip}{.75em}


\begin{multicols}{2}
[ \section{Identifying Losses}]

\newthought{Definition}

Accident: An undesired or unplanned event that results in a \textbf{loss}, including loss of human life or human injury, property damage, environmental pollution, mission loss, etc. [\emph{Engineering A Safer World} p 181]

\textbf{Losses} are the outcomes we want to prevent.

Our task is to \textbf{write a list} of them, staying broadly general and covering all the areas of concern for our safety analysis to address.
\newthought{Thermostat Example}

\input{examples/thermostat/losses}
 \columnbreak

\newthought{Desired Qualities} 
\begin{itemize}
\setlength{\itemsep}{0pt}
\setlength{\parskip}{.25em}
\item Concise --- We want a relatively short list (<20); these are our priorities.
\item General --- We don't want to prematurely narrow our focus. 

Example: "Someone is injured" may be a more useful loss statement than "Someone is injured by hot equipment" because, overall, we want to prevent \emph{any} injury.
\item Good coverage --- For any accident we can think up, we want it to be described by at least one of the losses on this list.
\item Non-redundant --- Overlap between losses is ok, but if one loss is entirely a subset of another, perhaps consider consolidating them.
\item Relevant --- They should be problems we actually consider important to prevent for our system. 

Example: "Civil war breaks out" is not a loss relevant to our thermostat example (except jokingly, or if there's an allegory about climate change).
\end{itemize}  
 
\newthought{Strategic Approaches} 

Ask "what is \emph{unacceptable}?" vs. "what is \emph{risky but tolerable}?" to distinguish from hazards.

\emph{Toolkit}: List of generic losses.

\newthought{Relationship to other concepts}

For each of these \textbf{losses}, we will identify hazardous system conditions that, in combination with environmental conditions, can result in an accident in which we experience the loss.

The relationship between \textbf{losses} and \textbf{hazards} lets us \emph{prioritize} our safety efforts, focusing on preventing the system states that are relevant to producing these accidents--- we don't need to examine every combination of system states.

\end{multicols}
\end{landscape}
\end{document}