
\textbf{Unsafe Control Action}: Turning the heat ON when the room is already too hot.

\textbf{Causal Scenarios}:

\begin{compactitem}
\item Control input or external info is wrong or missing:
  
  TARGET temperature is not set by the user and the default is unusually high.
  TARGET temperature is set to the wrong value; the user believed the input was in Farenheit, but the thermostat was using Celsius.  

\item Controller: Inadequate Control Algorithm.
  
Too long a delay between when thermostat measures temperatures and when it acts, so that the room has heated up (e.g. due to warm sunlight) before the thermostat turns the heater on.  
\item Controller: Process Model Inconsistent, incomplete, or incorrect.

  Perhaps the controller is storing temperature in Celsius, while the TARGET temperature is in Farenheit.
  Perhaps only two digits of temperature are stored and the room is 103F.
\item Inadequate or missing feedback:

  Thermometer uses different units than the thermostat, reporting degrees C which are recorded as degrees F.
  Thermometer is disconnected and the thermostat has not updated its MEASURED temperature.
%\item Feedback Delays
%
%MEASURED temperature is consistently delayed. MEASURED(t) temperature is ACTUAL(t-Delta). MEASURED temperature is inconsistently delayed.
 \item Sensor: inadequate operation; incorrect or no information provided

   Perhaps the thermometer is in an unusually cold location, unrepresentative of the general room temperature, so the thermostat activates the heat even when the room at large is already warm.
\end{compactitem}

\columnbreak
Other examples, not necessarily relevant to this action:

\begin{compactitem}
\item Controlled Process: Component failures
   
Furnace is broken. Furnace is out of fuel.
   \item Unidentified or out-of-range disturbance
   
Water in the basement, missing roof or walls, open windows
\item Actuator: Inadequate operation

  Heater failed to turn HEAT ON when signaled. Baseboards not radiating heat. Leaking water. Frozen pipes.

\item Controller 2: Conflicting control actions

Perhaps someone manually turned the heater on, circumventing the thermostat.
\end{compactitem}
